Future Directions

### 2021-03-01 manuscripts/laplacian_smoothing/AISTATS/minimax_optimal_laplacian_smoothing.tex
Fix typo, bib copyedit

\begin{lemma}
	\label{lem:neighborhood_eigenvalue} 
  There are constants $N,C_1,C_3,c_1,c_3 > 0$ such that for $n \geq N$, $C_0(\log n/n)^{1/d} \leq r \leq c_0$, and $f \in H^1(\Xset)$, with probability at least $1 - C_1n\exp(-c_1nr^d)$, it holds that
	\begin{equation}
	\label{eqn:neighborhood_eigenvalue}
	c_3A_{n,r}(k) \leq \lambda_k \leq C_3A_{n,r}(k), ~~\textrm{for $2 \leq k \leq n$},
	\end{equation}
where \smash{$A_{n,r}(k) = \min\{nr^{d + 2}k^{2/d},nr^d\}$}.
\end{lemma}

>>>>

\begin{lemma}
	\label{lem:neighborhood_eigenvalue} 
  There are constants $N,C_1,C_3,c_1,c_3 > 0$ such that for $n \geq N$ and $C_0(\log n/n)^{1/d} \leq r \leq c_0$, with probability at least $1 - C_1n\exp(-c_1nr^d)$, it holds that
	\begin{equation}
	\label{eqn:neighborhood_eigenvalue}
	c_3A_{n,r}(k) \leq \lambda_k \leq C_3A_{n,r}(k), ~~\textrm{for $2 \leq k \leq n$},
	\end{equation}
where \smash{$A_{n,r}(k) = \min\{nr^{d + 2}k^{2/d},nr^d\}$}.
\end{lemma}
